
\section{Background}
\label{sec:Background}

% K: fixme

\subsection{Event-B}
% K1: add \cite{..} to reference sources
% X: to be added later
Event-B is a formal method for system-level modelling and analysis~\cite{FIXME:something from Abrial}. Event-B uses a notation resembling  set theory for modeling systems and stepwise refinement to connect systems at different levels of abstraction. Mathematical proofs are required to justify consistency of system models as well as the preservation of safety properties proved at higher levels of abstraction down to lower levels.\\
% K1: don't use \\
In Event-B, machines are built to describe the static properties and track the dynamic behavior of a model. For a machine $M$, the variables $V$ are declared in the \texttt{Variable} section. The type of the variables and also the additional constraints $I$ for the variables are declared in the \texttt{Invariants} section.
% K1 etc. fix yourself following the previous paragraph. everything math goes between $s. Ensure consistent notationalt conventions. (E.g. "INITIALIZATION" doesn't wash with "Variable" above.)
The possible state changes for the machine is defined by events. For an event E, additional external variables t are introduced in the \texttt{Parameter} section. The preconditions G which enable an event’s execution are given by guards. The actions A implement the detailed changing between pre state and after state. Proofs are required to ensure the after state satisfy the invariants.\\
Every machine in Event-B must have an event INITIALIZATION ($E_{0}$) to set all the variables as the model start. $E_{0}$ does not have any guards nor parameters and the actions must cover the setup for all the variables.\\
However, in Event-B, only one event can happen at a time, which means original Event-B does not support concurrent execution.\\
In the rest parts of the thesis report, we will use following notions:\\
$M$ : Machine\\
$v$ : Variables\\
$J$ : Invariant\\
For all event $i$ $\in$ $I$, $I$ is the set of all events\\
$E_{i}$ : The event $i$, where $E_0$ is the INITIALIZATION event\\
$g_{i}$: The guard of Event $i$\\
$a_{i}$: The action of Event $i$\\
Since the event INITIALIZATION is different to the others, and can be executed once only. We introduce set $I_1$ to store the events other than INITIALIZATION.
\begin{displaymath}
  I = I_1\cap\{{0}\}
\end{displaymath}
\subsection{Temporal Logic}

% K1: all temporal logics are modal as far as I know
Temporal logic is a system of rules and symbolism for representing, and reasoning about, propositions qualified in terms of time. With modalities referring to time, linear temporal logic or linear-time temporal logic (LTL) is a modal temporal logic. In LTL, we can encode formulas about the future of paths, one example of this is "one condition will be always true after the system satisfy another condition". Some LTL notations we will use in the rest parts of this thesis report are:\\
$\Always\phi$	Globally: $\phi$ always happen (hold on the entire subsequent path)\\
$\Eventually\phi$	Finally: $\phi$ eventually happen (hold somewhere on the subsequent path)\\
$\Next\phi$	Next: $\phi$ will happen next (hold at next state)\\
In Event-B, $\phi$ can be a state of the machine, or a status that an event is chosen to be executed.\\
The LTL for a system is defined under the assumption of infinite execution. It does not make any sense for using LTL in a finite execution system (a system will automatic halt after limited executions).\\

% K1: I suspect you need to be more precise about executions of Event-B models in order to state formally what you mean